Code used to generate paper results : Database comparison and CT characteristics

### 2024-05-22 Paper_code-CT_analysis.Rmd
Changed some figures

```{r load_data, warning=FALSE, message=FALSE}
# CCLE_data <- CTdata::CCLE_data()
# TCGA_TPM <- CTdata::TCGA_TPM()
# testis_sce <- CTdata::testis_sce()
####

load("../CTdata/eh_data/all_genes.rda")
load("../CTdata/eh_data/GTEX_data.rda")
load("../CTdata/eh_data/CCLE_data.rda")
load("../CTdata/eh_data/TCGA_TPM.rda")
load("../CTdata/eh_data/normal_tissues_multimapping_data.rda")
load("../CTdata/eh_data/mean_methylation_in_tissues.rda")
load("../CTdata/eh_data/DAC_treated_cells_multimapping.rda")
load("../CTdata/eh_data/DAC_treated_cells.rda")
load("../CTdata/eh_data/testis_sce.rda")
load("../CTdata/eh_data/FGC_sce.rda")
load("../CTdata/eh_data/oocytes_sce.rda")

@@

```{r, eval = FALSE, echo=FALSE}
pdf(file = paste0("figs/GTEX_Tumors.pdf"))
draw(h_list, main_heatmap = "TCGA (logTPM)", 
     ht_gap = unit(c(0.3, 0.01), "cm"),
     merge_legend = TRUE)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Multimapping.pdf"))
draw(h_list, main_heatmap = "log(TPM)", ht_gap = unit(0.3, "cm"),
                 height = unit(5, "cm"))
dev.off()
```

@@

  h <- Heatmap(mat[gene_type$gene, sort(colnames(mat))],
               column_title = "Promoter methylation",
               name = "Mean \nmethylation",
               column_title_gp = gpar(fontsize = 6),
               border = TRUE,
               border_gp = gpar(lwd = 0.5),
               row_title_gp = gpar(col = c("indianred2", "cyan4"), fontsize = 6),
               row_split = factor(gene_type$Regulation,
                                  levels = c("Methylation", "Not methylation")),
               #row_split = factor(gene_type$group),
               cluster_row_slices = FALSE,
               col = colorRamp2(seq_len(100),
                                colorRampPalette(c("moccasin", "dodgerblue4"))(100)),
               na_col = "gray80",
               cluster_rows = FALSE,
               cluster_columns = FALSE,
               show_row_names = TRUE,
               show_heatmap_legend = TRUE,
               show_row_dend = FALSE,
               column_names_gp = gpar(fontsize = column_fontsize),
               row_names_gp = gpar(fontsize = row_fontsize),
               row_names_side = "left",
               heatmap_width = unit(4, "cm"),
               heatmap_height = unit(10, "cm"),
               use_raster = TRUE,
               raster_device = "CairoPNG",
               raster_quality = 8,
               column_names_side = "top",
               heatmap_legend_param = legends_param)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Methylation_classification.pdf"))
draw(h_list, main_heatmap = "Mean \nmethylation", ht_gap = unit(0.5, "cm"), 
     merge_legend = TRUE)
dev.off()
```

@@

```{r, eval = FALSE, echo=FALSE}
pdf(file = paste0("figs/X_enrichment.pdf"), width = 7, height = 4)
cowplot::plot_grid(met_prop_fig, fig_X_enrichment, labels = c('A', 'B'), 
          rel_widths = c(1, 2),
          label_size = 12)
dev.off()
```

@@

prop.table(table(CT_genes$transcript_biotype,
                 methylation = CT_genes$regulated_by_methylation))
```
# CT genes in tumour : coexpression and link with global hypomethylation

@@

fig_mean_prop_in_tum <- ggplot(mean_and_prop[!is.na(mean_and_prop$Regulation), ],
                               aes(x = mean_log, y = proportion_of_positive_tum,
                                   shape = X_linked,
                                   color = Regulation,
                                   label = gene)) +
  geom_point(size = 1) +
  scale_colour_manual(values = Regulation_colors)+
  ggrepel::geom_text_repel(
    data = mean_and_prop %>% 
      filter(proportion_of_positive_tum > 20 | 
               (proportion_of_positive_tum > 5 & mean_log > 4)), 
    aes(x = mean_log, y = proportion_of_positive_tum, 
        label = gene), size = 1.5, color = "black", min.segment.length = 1,
    max.overlaps = 30, direction = "both") +
  xlab("Mean expression log(TPM + 1)\nin positive samples") +
  ylab("Proportion of positive samples (%)") +
  facet_wrap(~ source, ncol = 1) +
  theme_bw() +
  theme(legend.position = "right",
        aspect.ratio = 0.8,
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.key.size = unit(0.3, 'cm'),
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        axis.text = element_text(size = 5),
        axis.ticks = element_line(size = 0.1),
        axis.title = element_text(size = 6),
        strip.text = element_text(size = 6))

fig_mean_prop_in_tum
```
```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Mean_prop_in_tumors.pdf"), width = 5, height = 4)
fig_mean_prop_in_tum
dev.off()
```

@@

```{r, echo = FALSE, eval = FALSE}
pdf(file = "figs/CT_met_AUC_hypo_TCGA.pdf", height = 2.3, width = 3)
draw(h1, column_title = "CT genes regulated by methylation",
     column_title_gp = gpar(fontsize = 5), show_heatmap_legend = FALSE,
     show_annotation_legend = FALSE)
dev.off()

@@

```{r}
pdf(file = paste0("figs/CT_met_AUCscore_hypo_TCGA.pdf"), height = 2.5)
f1
dev.off()

@@

```{r, testis_data}
################################################################################
# Load testis scRNAseq data
################################################################################

@@

################################################################################
# Load FGC and oocytes scRNAseq data
################################################################################

@@

legends_param_sc <- list(
  labels_gp = gpar(col = "black", fontsize = 2),
  title_gp = gpar(col = "black", fontsize = 3),
  simple_anno_size = unit(0.15, "cm"),
  row_names_gp = gpar(fontsize = 1),
  annotation_name_side = "left",
  border = FALSE,
  border_gp = gpar(lwd = 0.01),
  grid_width = unit(0.2, "cm"),
  grid_height = unit(0.2, "cm"),
  legend_height = unit(0.1, "cm"),
  annotation_name_gp = gpar(fontsize = 0))

@@

```{r healthy_cells_function}
#######################################################################
# Function to downsample cell types
#######################################################################
sample_cells <- function(barcodes, nmax){
  sample(barcodes, size = min(nmax, length(barcodes)), replace = FALSE)
}

#######################################################################
## Function to draw expression in FGC with specific annotations
## and downasampling the number of cells from each cell type
#######################################################################
draw_FGC_heatmap <- function(genes, 
                             split_by = "chr_met", 
                             ncells_max = NULL,
                             scale_lims = NULL,
                             sex = c("F", "M"),
                             clusterRow = FALSE, 
                             font_size = 6,
                             show_legend = TRUE,
                             h_width = 5,
                             h_height = 10,
                             show_right_annot = TRUE){

@@

  if (!show_right_annot) rAnnot <- NULL

@@

  ht_FGCs <- Heatmap(mat,
                     name = "Logcounts",
                     column_title = title,
                     column_split = df_col_FCS$type,
                     cluster_row_slices = FALSE,
                     cluster_column_slices = FALSE,
                     col = heatmap_colors,
                     border = TRUE,
                     border_gp = gpar(lwd = 0.2),
                     row_gap = unit(c(1), "mm"),
                     column_gap = unit(c(0.5), "mm"),
                     show_column_dend = FALSE,
                     show_row_dend = FALSE,
                     row_names_gp = gpar(fontsize = font_size),
                     row_names_side = "left",
                     cluster_rows = clusterRow,
                     cluster_columns = FALSE,
                     show_column_names = FALSE,
                     show_row_names = FALSE,
                     row_split = rowSplit,
                     top_annotation = c(column_ha_sex, 
                                        column_ha_stage,
                                        #column_ha_group, 
                                        #column_ha_donor_id,
                                        column_ha_type),  
                     right_annotation = rAnnot,
                     column_title_gp = gpar(fontsize = 5),
                     row_title_gp = gpar(fontsize = 0),
                     gap = unit(0.01, "mm"),
                     use_raster = TRUE,
                     raster_device = "CairoPNG",
                     #heatmap_width = unit(h_width, "cm"),
                     #heatmap_height = unit(h_height, "cm"),
                     raster_quality = 10,
                     show_heatmap_legend = show_legend,
                     heatmap_legend_param = legends_param_sc)

@@

################################################################################
## Function to draw expression in adult testis cells with specific annotations
## and downasampling the number of cells from each cell type
################################################################################
draw_testis_heatmap <- function(genes, 
                                split_by = "chr_met", 
                                sex = c("F", "M"),
                                ncells_max = NULL,
                                font_size = 6,
                                scale_lims = NULL,
                                clusterRow = FALSE,
                                show_legend = TRUE,
                                h_width = 5,
                                h_height = 10,
                                clust_method = "ward.D"){

@@

@@

  ht_testis <- Heatmap(mat,
                       name = "logcounts",
                       column_title = "Adult testis",
                       column_split = df_col_testis$type,
                       row_title = NULL,
                       col = heatmap_colors,
                       border = TRUE,
                       border_gp = gpar(lwd = 0.2),
                       row_gap = unit(c(0.5), "mm"),
                       column_gap = unit(c(0.5), "mm"),
                       show_column_dend = FALSE,
                       show_row_dend = FALSE,
                       row_names_gp = gpar(fontsize = font_size),
                       row_names_side = "right",
                       cluster_rows = clusterRow,
                       clustering_method_rows = clust_method,
                       row_dend_reorder = TRUE,
                       cluster_columns = FALSE,
                       show_column_names = FALSE,
                       show_row_names = TRUE,
                       row_split = rowSplit,
                       cluster_row_slices = FALSE,
                       cluster_column_slices = FALSE,
                       top_annotation = c(column_ha_sex, 
                                          column_ha_stage,
                                          column_ha_cell_type),  
                       right_annotation = c(row_ha_regulation, 
                                            row_ha_chr, 
                                            gap = unit(1, "mm")),
                       column_title_gp = gpar(fontsize = 5),
                       row_title_gp = gpar(fontsize = 0),
                       gap = unit(0.01, "mm"),
                       use_raster = TRUE,
                       raster_device = "CairoPNG",
                       raster_quality = 10,
                       #heatmap_width = unit(h_width, "cm"),
                       #heatmap_height = unit(h_height, "cm"),
                       show_heatmap_legend =  show_legend,
                       heatmap_legend_param = legends_param_sc)

@@

################################################################################
## Function to draw expression in adult oocytes cells with specific annotations
## and downasampling the number of cells from each cell type
################################################################################
draw_oocytes_heatmap <- function(genes, 
                               split_by = "chr_met", 
                               ncells_max = NULL,
                               font_size = 6,
                               scale_lims = NULL,
                               clusterRow = TRUE,
                               show_legend = TRUE,
                               h_width = 5,
                               h_height = 10,
                               clust_method = "ward.D"){

@@

fs <- 2
ncells <- 100
scale_limits <- c(0, 4)
ht_testis <- draw_testis_heatmap(my_genes,
                    ncells_max = ncells,
                    font_size = fs,
                    scale_lims = scale_limits,
                    clusterRow  = FALSE,
                    split_by = "chr_met",
                    show_legend = TRUE,
                    clust_method = "ward.D2")

female_FGC_ht <- draw_FGC_heatmap(my_genes, 
                 ncells_max = ncells,
                 sex = c("F"),
                 clusterRow = FALSE, 
                 font_size = fs,
                 scale_lims = scale_limits, 
                 show_legend = FALSE,
                 show_right_annot = FALSE)

male_FGC_ht <- draw_FGC_heatmap(my_genes, 
                 ncells_max = ncells,
                 sex = c("M"),
                 clusterRow = FALSE, 
                 font_size = fs,
                 scale_lims = scale_limits, 
                 show_legend = FALSE,
                 show_right_annot = FALSE)

@@

ht_list <- female_FGC_ht + ht_oocytes + male_FGC_ht + ht_testis
draw(ht_list, main_heatmap = "logcounts", merge_legend = TRUE, ht_gap = unit(0.2, "cm"))

@@

```{r, echo = FALSE, eval = FALSE}
pdf(file = paste0("figs/CT_in_GermCells.pdf"), width = 6, height = 4)
draw(ht_list, main_heatmap = "Logcounts", 
     merge_legend = TRUE, 
     ht_gap = unit(0.2, "cm"), 
     legend_gap = unit(0.15, "cm"),
     legend_grid_height = unit(0.08, "cm"),
    legend_grid_width = unit(0.1, "cm"))
dev.off()
```

## Gene function

>>>>

```{r load_data, warning=FALSE, message=FALSE}
load("../CTdata/eh_data/all_genes.rda")
load("../CTdata/eh_data/GTEX_data.rda")
load("../CTdata/eh_data/CCLE_data.rda")
load("../CTdata/eh_data/TCGA_TPM.rda")
load("../CTdata/eh_data/normal_tissues_multimapping_data.rda")
load("../CTdata/eh_data/mean_methylation_in_tissues.rda")
load("../CTdata/eh_data/DAC_treated_cells_multimapping.rda")
load("../CTdata/eh_data/DAC_treated_cells.rda")
load("../CTdata/eh_data/testis_sce.rda")
load("../CTdata/eh_data/FGC_sce.rda")
load("../CTdata/eh_data/oocytes_sce.rda")

@@

```{r, eval = TRUE, echo=FALSE}
pdf(file = paste0("figs/GTEX_Tumors.pdf"))
draw(h_list, main_heatmap = "TCGA (logTPM)", 
     ht_gap = unit(c(0.3, 0.01), "cm"),
     merge_legend = TRUE)
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Multimapping.pdf"))
draw(h_list, main_heatmap = "log(TPM)", ht_gap = unit(0.3, "cm"),
                 height = unit(5, "cm"))
dev.off()
```

@@

  h <- Heatmap(mat[gene_type$gene, sort(colnames(mat))],
               column_title = "Promoter methylation",
               name = "Mean \nmethylation",
               column_title_gp = gpar(fontsize = 6),
               border = TRUE,
               border_gp = gpar(lwd = 0.5),
               row_title_gp = gpar(col = c("indianred2", "cyan4"), fontsize = 8),
               row_split = factor(gene_type$Regulation,
                                  levels = c("Methylation", "Not methylation")),
               #row_split = factor(gene_type$group),
               cluster_row_slices = FALSE,
               col = colorRamp2(seq_len(100),
                                colorRampPalette(c("moccasin", "dodgerblue4"))(100)),
               na_col = "gray80",
               cluster_rows = FALSE,
               cluster_columns = FALSE,
               show_row_names = TRUE,
               show_heatmap_legend = TRUE,
               show_row_dend = FALSE,
               column_names_gp = gpar(fontsize = column_fontsize),
               row_names_gp = gpar(fontsize = row_fontsize),
               row_names_side = "left",
               heatmap_width = unit(4, "cm"),
               heatmap_height = unit(10, "cm"),
               use_raster = TRUE,
               raster_device = "CairoPNG",
               raster_quality = 8,
               column_names_side = "top",
               heatmap_legend_param = legends_param)

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Methylation_classification.pdf"))
draw(h_list, main_heatmap = "Mean \nmethylation", ht_gap = unit(0.5, "cm"), 
     merge_legend = TRUE)
dev.off()
```

@@

```{r, eval = TRUE, echo=FALSE}
pdf(file = paste0("figs/X_enrichment.pdf"), width = 7, height = 4)
cowplot::plot_grid(met_prop_fig, fig_X_enrichment, labels = c('A', 'B'), 
          rel_widths = c(1, 2),
          label_size = 12)
dev.off()
```

@@

prop.table(table(CT_genes$transcript_biotype,
                 methylation = CT_genes$regulated_by_methylation))
```

# CT genes in tumour : coexpression and link with global hypomethylation

@@

fig_mean_prop_in_tum <- ggplot(mean_and_prop[!is.na(mean_and_prop$Regulation), ],
                               aes(x = mean_log, y = proportion_of_positive_tum,
                                   shape = X_linked,
                                   color = Regulation,
                                   label = gene)) +
  geom_point(size = 1) +
  scale_colour_manual(values = Regulation_colors)+
  ggrepel::geom_text_repel(
    data = mean_and_prop %>% 
      filter(proportion_of_positive_tum > 20 | 
               (proportion_of_positive_tum > 5 & mean_log > 4)), 
    aes(x = mean_log, y = proportion_of_positive_tum, 
        label = gene), size = 1.5, color = "black", min.segment.length = 1,
    max.overlaps = 30, direction = "both") +
  xlab("Mean expression log(TPM + 1)\nin positive samples") +
  ylab("Proportion of positive samples (%)") +
  facet_wrap(~ source, ncol = 2) +
  theme_bw() +
  theme(legend.position = "right",
        aspect.ratio = 0.8,
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.key.size = unit(0.3, 'cm'),
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        axis.text = element_text(size = 5),
        axis.ticks = element_line(size = 0.1),
        axis.title = element_text(size = 6),
        strip.text = element_text(size = 6))

fig_mean_prop_in_tum
```
```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Mean_prop_in_tumors.pdf"), width = 5, height = 4)
fig_mean_prop_in_tum
dev.off()
```

@@

```{r, echo = FALSE, eval = TRUE}
pdf(file = "figs/CT_met_AUC_hypo_TCGA.pdf", height = 2.3, width = 3)
draw(h1, column_title = "CT genes regulated by methylation",
     column_title_gp = gpar(fontsize = 5), show_heatmap_legend = TRUE,
     show_annotation_legend = TRUE, heatmap_legend_side = "bottom",
     merge_legend = TRUE)
dev.off()

@@

```{r, echo = FALSE}
pdf(file = paste0("figs/CT_met_AUCscore_hypo_TCGA.pdf"), height = 2.5)
f1
dev.off()

@@

```{r testis_data}
# Load testis scRNAseq data

@@

## Load FGC and oocytes scRNAseq data

@@

legends_param_sc <- list(
  labels_gp = gpar(col = "black", fontsize = 3),
  title_gp = gpar(col = "black", fontsize = 4),
  simple_anno_size = unit(0.15, "cm"),
  row_names_gp = gpar(fontsize = 1),
  annotation_name_side = "left",
  border = FALSE,
  border_gp = gpar(lwd = 0.01),
  grid_width = unit(0.2, "cm"),
  grid_height = unit(0.2, "cm"),
  legend_height = unit(0.1, "cm"),
  annotation_name_gp = gpar(fontsize = 0))

@@

```{r healthy_cells_function}

# Function to downsample cell types

sample_cells <- function(barcodes, nmax){
  sample(barcodes, size = min(nmax, length(barcodes)), replace = FALSE)
}

## Function to draw expression in FGC with specific annotations
## and downasampling the number of cells from each cell type

draw_FGC_heatmap <- function(genes, 
                             split_by = "chr_met", 
                             ncells_max = NULL,
                             scale_lims = NULL,
                             sex = c("F", "M"),
                             clusterRow = FALSE, 
                             font_size = 6,
                             show_legend = TRUE,
                             h_width = 5,
                             h_height = 10,
                             show_row_annot = TRUE, 
                             row_title = TRUE){

@@

  if (!show_row_annot) rAnnot <- NULL

  if (row_title) rtitle <- gpar(fontsize = 5, fontface = "bold") else rtitle <- gpar(fontsize = 0)

@@

  ht_FGCs <- Heatmap(mat,
                     name = "Logcounts",
                     column_title = title,
                     column_split = df_col_FCS$type,
                     cluster_row_slices = FALSE,
                     cluster_column_slices = FALSE,
                     col = heatmap_colors,
                     border = TRUE,
                     border_gp = gpar(lwd = 0.2),
                     row_gap = unit(c(1), "mm"),
                     column_gap = unit(c(0.5), "mm"),
                     show_column_dend = FALSE,
                     show_row_dend = FALSE,
                     row_names_gp = gpar(fontsize = font_size),
                     row_names_side = "left",
                     cluster_rows = clusterRow,
                     cluster_columns = FALSE,
                     show_column_names = FALSE,
                     show_row_names = FALSE,
                     row_split = rowSplit,
                     top_annotation = c(column_ha_sex, 
                                        column_ha_stage,
                                        #column_ha_group, 
                                        #column_ha_donor_id,
                                        column_ha_type),  
                     left_annotation = rAnnot,
                     column_title_gp = gpar(fontsize = 5),
                     row_title_gp = rtitle,
                     gap = unit(0.01, "mm"),
                     use_raster = TRUE,
                     raster_device = "CairoPNG",
                     #heatmap_width = unit(h_width, "cm"),
                     #heatmap_height = unit(h_height, "cm"),
                     raster_quality = 10,
                     show_heatmap_legend = show_legend,
                     heatmap_legend_param = legends_param_sc,
                     row_title_rot = 0)

@@

## Function to draw expression in adult testis cells with specific annotations
## and downasampling the number of cells from each cell type

draw_testis_heatmap <- function(genes, 
                                split_by = "chr_met", 
                                sex = c("F", "M"),
                                ncells_max = NULL,
                                font_size = 6,
                                scale_lims = NULL,
                                clusterRow = FALSE,
                                show_legend = TRUE,
                                h_width = 5,
                                h_height = 10,
                                clust_method = "ward.D",
                                show_row_annot = TRUE){

@@

  if (!show_row_annot) rAnnot <- NULL

@@

  ht_testis <- Heatmap(mat,
                       name = "logcounts",
                       column_title = "Adult testis",
                       column_split = df_col_testis$type,
                       row_title = NULL,
                       col = heatmap_colors,
                       border = TRUE,
                       border_gp = gpar(lwd = 0.2),
                       row_gap = unit(c(0.5), "mm"),
                       column_gap = unit(c(0.5), "mm"),
                       show_column_dend = FALSE,
                       show_row_dend = FALSE,
                       row_names_gp = gpar(fontsize = font_size),
                       row_names_side = "right",
                       cluster_rows = clusterRow,
                       clustering_method_rows = clust_method,
                       row_dend_reorder = TRUE,
                       cluster_columns = FALSE,
                       show_column_names = FALSE,
                       show_row_names = TRUE,
                       row_split = rowSplit,
                       cluster_row_slices = FALSE,
                       cluster_column_slices = FALSE,
                       top_annotation = c(column_ha_sex, 
                                          column_ha_stage,
                                          column_ha_cell_type),  
                       right_annotation = rAnnot,
                       column_title_gp = gpar(fontsize = 5),
                       row_title_gp = gpar(fontsize = 0),
                       gap = unit(0.01, "mm"),
                       use_raster = TRUE,
                       raster_device = "CairoPNG",
                       raster_quality = 10,
                       #heatmap_width = unit(h_width, "cm"),
                       #heatmap_height = unit(h_height, "cm"),
                       show_heatmap_legend =  show_legend,
                       heatmap_legend_param = legends_param_sc)

@@

## Function to draw expression in adult oocytes cells with specific annotations
## and downasampling the number of cells from each cell type

draw_oocytes_heatmap <- function(genes, 
                               split_by = "chr_met", 
                               ncells_max = NULL,
                               font_size = 6,
                               scale_lims = NULL,
                               clusterRow = TRUE,
                               show_legend = TRUE,
                               h_width = 5,
                               h_height = 10,
                               clust_method = "ward.D"){

@@

fs <- 2
ncells <- 100
scale_limits <- c(0, 4)
ht_testis <- draw_testis_heatmap(my_genes,
                    ncells_max = ncells,
                    font_size = fs,
                    scale_lims = scale_limits,
                    clusterRow  = FALSE,
                    split_by = "chr_met",
                    show_legend = TRUE,
                    clust_method = "ward.D2",
                    show_row_annot = FALSE)

female_FGC_ht <- draw_FGC_heatmap(my_genes, 
                 ncells_max = ncells,
                 sex = c("F"),
                 clusterRow = FALSE, 
                 font_size = fs,
                 scale_lims = scale_limits, 
                 show_legend = FALSE,
                 show_row_annot = TRUE,
                 row_title = TRUE)

male_FGC_ht <- draw_FGC_heatmap(my_genes, 
                 ncells_max = ncells,
                 sex = c("M"),
                 clusterRow = FALSE, 
                 font_size = fs,
                 scale_lims = scale_limits, 
                 show_legend = FALSE,
                 show_row_annot = FALSE,
                 row_title = FALSE)

@@

ht_list <- female_FGC_ht + ht_oocytes + male_FGC_ht + ht_testis
draw(ht_list, main_heatmap = "Logcounts", merge_legend = TRUE, 
     ht_gap = unit(0.2, "cm"))

@@

```{r, echo = FALSE, eval = TRUE}
pdf(file = paste0("figs/CT_in_GermCells.pdf"), width = 6, height = 4)
draw(ht_list, main_heatmap = "Logcounts", 
     merge_legend = TRUE, 
     ht_gap = unit(0.2, "cm"), 
     legend_gap = unit(0.15, "cm"),
     legend_grid_height = unit(0.08, "cm"),
    legend_grid_width = unit(0.1, "cm"))
dev.off()
```

# Gene function
